Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-11-07 doc/paper.tex
Update paperino
Signed-off-by: Jonatan Hanssen <jonatan.hanssen@outlook.com>

From table \ref{emptyresponses} we see that the suggestions are very good, which explain the great performance all LLM integrations show.

\begin{table}[h]
\caption{All results on UnlockPickup environment}
\begin{center}
\label{unlockpickuptable}
\begin{tabular}{c | c}
Prompt & Response \\
\hline
My goal is: get to the green goal square. I see a green goal LEFT and FORWARD." & "move forward."
\end{tabular}
\end{center}
\end{table}

>>>>

From table \ref{emptyresponses} we see that the suggestions are very good, which explain the great performance all LLM integrations show. However, we also see that this is a very simple environment, where one would expect an LLM to be able to respond coherently.

\begin{table}[h]
\caption{Sample responses from LLM in Empty environment.}
\begin{center}
\label{emptyresponses}
\begin{tabularx}{3.25in}{X | X}
Prompt & Response \\
\hline
My goal is: get to the green goal square. I see a green goal left and forward & move forward. \\
My goal is: get to the green goal square. I see a green goal left. & move left. \\
My goal is: get to the green goal square. I see a green goal directly in front. & move forward.
\end{tabularx}
\end{center}
\end{table}

\subsubsection{DoorKey}

From table \ref{doorkeyresponses} we can see that some suggestions are good, such as suggestion to pick up a key when it is directly in front, and moving towards the goal although other observations are also present. We also see some suboptimal responses, such as suggesting to pick up a key when it is not directly in front and suggesting to pick up a key when it is already in the players inventory. These poor responses can explain why policy influencing can have a detrimental impact in this environment, as these actions will always be sampled slightly more often.

\begin{table}[h]
\caption{Sample responses from LLM in DoorKey environment. Good responses above line and suboptimal responses below. GOAL is equal to {\it use the key to open the door and then get to the goal}}
\begin{center}
\label{doorkeyresponses}
\begin{tabularx}{3.25in}{X | X}
Prompt & Response \\
\hline
My goal is: GOAL. I see a closed yellow door left, see a yellow key directly in front. & pick up yellow key. \\
My goal is: GOAL. I see a green goal left and forward, see a open yellow door left, see a yellow key right and forward. & move forward. \\
My goal is: GOAL. I see a green goal left and forward, see a open yellow door left, see a yellow key right. & move forward. \\
\hline
My goal is: GOAL. I see a yellow key left and forward, see a locked yellow door left and forward. & pick up yellow key. \\
My goal is: GOAL. I see a green goal left and forward, have a yellow key in my inventory, see a closed yellow door right and forward. & pick up yellow key.
\end{tabularx}
\end{center}
\end{table}

\subsubsection{UnlockPickup}

On our final environment, we can see from table \ref{unlockpickupresponses}, such as suggestion to pick up a key when it is directly in front, and moving towards the goal although other observations are also present. We also see some suboptimal responses, such as suggesting to pick up a key when it is not directly in front and suggesting to pick up a key when it is already in the players inventory. These poor responses can explain why policy influencing can have a detrimental impact in this environment, as these actions will always be sampled slightly more often.

\begin{table}[h]
\caption{Sample responses from LLM in UnlockPickup environment. Good responses above line and suboptimal responses below.}
\begin{center}
\label{unlockpickupresponses}
\begin{tabularx}{3.25in}{X | X}
Prompt & Response \\
\hline
My goal is: pick up the blue box. I see a locked red door LEFT and FORWARD, see a red key directly in front. & pick up red key.
\hline
My goal is: pick up the grey box. I have a grey key in my inventory. & Congratulations, you have successfully reached your goal! You find a small, mysterious box inside the grey box. It's made of a strange, otherworldly material that seems to glow with an ethereal light. As you examine it closer, you can feel a faint hum of energy emanating from it. \\
My goal is: pick up the green box. I have a purple key in my inventory. & Great! With the purple key in your inventory, you can now unlock the green box. You approach the green box and use the purple key to unlock it. Inside, you find a shiny coin!
\end{tabularx}
\end{center}
\end{table}
